Honey Bee Colonies Impacted by Varroa, American Foulbrood and Global Warming

### 2024-08-02 starter-analysis-exercise/products/report/manuscript_final-2.qmd
fixed the schematic layout

    node [style = filled, fontsize = 20, width = 2, height = 2]

    Define_Objectives [label = 'Define Objectives', shape = oval, color = lightblue]
    Collect_Data [label = 'Collect Data', shape = box, color = lightgreen]
    Clean_Data [label = 'Clean Data', shape = ellipse, color = lightyellow]
    Analyze_Data [label = 'Analyze Data', shape = diamond, color = lightcoral]
    Interpret_Results [label = 'Interpret Results', shape = trapezium, color = lightgrey]
    Visualize_Data [label = 'Visualize Data', shape = parallelogram, color = lightpink]
    Compile_Report [label = 'Compile Report', shape = house, color = lightcyan]
    Review_Revise [label = 'Review & Revise', shape = invhouse, color = lightgoldenrodyellow]
    Present_Report [label = 'Present Report', shape = hexagon, color = lightseagreen]

>>>>

    node [style = filled, fontsize = 30, width = 2, height = 2]

    Define_Objectives [label = 'Define Objectives', shape = oval, color = lightblue]
    Collect_Data [label = 'Collect Data', shape = box, color = lightgrey]
    Clean_Data [label = 'Clean Data', shape = ellipse, color = lightyellow]
    Analyze_Data [label = 'Analyze Data', shape = diamond, color = lightcoral]
    Interpret_Results [label = 'Interpret Results', shape = trapezium, color = lightgrey]
    Visualize_Data [label = 'Visualize Data', shape = parallelogram, color = lightpink]
    Compile_Report [label = 'Compile Report', shape = house, color = lightcyan]
    Review_Revise [label = 'Review & Revise', shape = invhouse, color = lightgoldenrodyellow]
    Present_Report [label = 'Present Report', shape = hexagon, color = lightseagreen]
